Nilpotent Invariants \\ for Generic Discrete Series of Real Groups

### 2025-12-22 revision_whittaker.tex
Fixes the typos mentioned in the report

Suppose $X\in i\g(\R)^*\subset \g^*$ is a regular nilpotent element (see Section \ref{s:dual}).
Let $\overline{\mathfrak b}(\R)$ be the kernel of $X$. This is the Lie algebra of~$\overline{B}(\R)$, where
$\overline{B}$ is an $\R$-Borel subgroup of~$G$.
Choose an $\R$-Cartan subgroup $T$ of
$\overline B$, and let~$B$ be the  Borel
subgroup opposite to~$\overline{B}$, characterized by $B\cap \overline B=T$.
Then $X$ defines a unitary
character of the nilradical  $N(\R)$  of $B(\R)$ by
\[ 
\psi_X(\exp Y)=e^{X(Y)}\quad (Y\in\n(\R)).
\] 
We define $\w_X$ to be the $G(\R)$-conjugacy class of $(B(\R),\psi_X)$; as the notation indicates this is independent 
of the choice of $T$.

@@

\subsubsection{The Sekiguchi correspondence for principal nilpotent orbits}\label{sec:concrete_sek}
Let us spell out the special case of the Sekiguchi correspondence which is of interest here. We follow~\cite[Section~2]{AVAV}.

Suppose $E_\R\in i\g(\R)$ is a principal nilpotent element.
We may choose $H_\R, E_\R \in \g$ such that $(H_\R,E_\R,F_\R)$ is an $\mathrm{SL}(2)$-triple and  $E_\R$  contained in $i\g(\R)$,
which implies $H_\R\in \g(\R)$. 
After conjugating by~$G(\R)$ we may further assume $\theta(E_\R)=-F_\R$. Set 
\[   E_\theta=\frac12(E_\R-F_\R+H_\R)\quad
F_\theta=\frac12(-E_\R+F_\R+H_\R).
\]
Then
$$
\KS(G(\R)\cdot E_\R)=K\cdot E_\theta.
$$
Computing the map in the other direction is similar. Suppose $E_\theta\in \s$ is a principal nilpotent element. 
Choose $F_\theta, H_\theta \in \g$ such that $(E_\theta, H_\theta, F_\theta)$ is an $SL(2)$-triple with $F_\theta \in \s$,  which implies $H_\theta\in\k$. After conjugating by $K$ we may further assume $\sigma(E_\theta)=F_\theta$.
Define 
\begin{equation}\label{def_F_R}
E_\R=\frac12(E_\theta-F_\theta-H_\theta)\quad
F_\R=\frac12(-E_\theta+F_\theta-H_\theta).
\end{equation}
Then
\begin{equation}
\label{e:KS}
\KS(K\cdot E_\theta)=G(\R)\cdot E_\R\quad\KS(K\cdot F_\theta)=G(\R)\cdot(-E_\R).
\end{equation}

>>>>

Suppose $X\in i\g(\R)^*\subset \g^*$ is a regular nilpotent element (see Section \ref{s:dual}).
Let $\overline{\mathfrak b}(\R)$ be the kernel of $X$ in $\g(\R)$. This is the Lie algebra of~$\overline{B}(\R)$, where
$\overline{B}$ is an $\R$-Borel subgroup of~$G$.
Choose an $\R$-Cartan subgroup $T$ of
$\overline B$, and let~$B$ be the  Borel
subgroup opposite to~$\overline{B}$, characterized by $B\cap \overline B=T$.
Then $X$ defines a unitary
character of the nilradical  $N(\R)$  of $B(\R)$ by
\[ 
\psi_X(\exp Y)=e^{X(Y)}\quad (Y\in\n(\R)).
\] 
We define $\w_X$ to be the $G(\R)$-conjugacy class of $(B(\R),\psi_X)$; as the notation indicates this is independent 
of the choice of $T$.

@@

\subsubsection{The Sekiguchi correspondence for principal nilpotent orbits}\label{sec:concrete_sek}

Let us spell out the special case of the Sekiguchi correspondence which is of interest here. We follow~\cite[Section~2]{AVAV}.

Suppose $E_\R\in i\g(\R)$ is a principal nilpotent element.
We may choose $H_\R, F_\R \in \g$ such that $(H_\R,E_\R,F_\R)$ is an $\mathrm{SL}(2)$-triple and  $E_\R$  contained in $i\g(\R)$,
which implies $H_\R\in \g(\R)$. 
After conjugating by~$G(\R)$ we may further assume $\theta(E_\R)=-F_\R$. Set 
\[   E_\theta=\frac12(E_\R-F_\R+H_\R)\quad
F_\theta=\frac12(-E_\R+F_\R+H_\R).
\]
Then
$$
\KS(G(\R)\cdot E_\R)=K\cdot E_\theta.
$$
Computing the map in the other direction is similar. Suppose $E_\theta\in \s$ is a principal nilpotent element. 
Choose $F_\theta, H_\theta \in \g$ such that $(E_\theta, H_\theta, F_\theta)$ is an $SL(2)$-triple with $F_\theta \in \s$,  which implies $H_\theta\in\k$. After conjugating by $K$ we may further assume $\sigma(E_\theta)=F_\theta$.
Define 
\begin{equation}\label{def_F_R}
E_\R=\frac12(E_\theta-F_\theta-H_\theta)\quad
F_\R=\frac12(-E_\theta+F_\theta-H_\theta).
\end{equation}
Then
\begin{equation}
\label{e:KS}
\KS(K\cdot E_\theta)=G(\R)\cdot E_\R\quad\KS(K\cdot F_\theta)=G(\R)\cdot(-E_\R).
\end{equation}
